$\text{Big}\times(\text{Science}+\underbracket{\cancel{\text{Data}}}_{\small \text{Imaging}})$ @ UVA

### 2013-02-08 SOMResearchRetreat2013/Presentation/presentation.tex
ENH:  UVA school of medicine research retreat presentation.

\documentclass[xcolor=dvipsnames,serif,10pt]{beamer}

@@

  \begin{columns}[c]
    \begin{column}{0.5\textwidth}
    \begin{center}  
      \includegraphics[width=5cm]{London_taxi.jpg}
    \end{center}
    \end{column}  
    \begin{column}{0.4\textwidth}
    \begin{center}  
      \vspace{-0.5cm}
      \pause
      \includegraphics[width=5cm]{hippocampus.png} \\
      \pause
        \begin{align*}
			  SPM (1995):\,\,&   6418\,\,\text{citations}\\
			  VBM (2000):\,\,&   3593\,\,\text{citations}\\
			  Opt. VBM (2001):\,\,&  2353\,\,\text{citations}\\
			  TBSS (2006):\,\,&  1106\,\,\text{citations}\\
			  \end{align*}
      \vspace{0cm}
			  \highlight[yellow!100!black]{$6418 + 3593 + 2353 + 1106 = 13470\,\,\text{citations}$}
    \end{center}
    \end{column}  
  \end{columns}    
\end{frame}

@@

\begin{frame}

\tikzset{level 1 concept/.append style={font=\sf, sibling angle=135,level distance = 25mm}}
\tikzset{level 2 concept/.append style={font=\sf, sibling angle=60,level distance = 15mm}}
\tikzset{level 3 concept/.append style={font=\sf, sibling angle=60,level distance = 15mm}}
\tikzset{every node/.append style={scale=0.5}}

\begin{center}
\resizebox{9cm}{7.5cm}{
\begin{tikzpicture}
  \path[mindmap,concept color=red!50!black,text=white]
    node[concept,scale=0.9] {\Large Data Analysis}
    [clockwise from=45]
    child[concept color=green!50!black, yshift=-0.5cm] {
      node[concept,scale=1.1] {Imaging Applications}
      [clockwise from=120]
      child[concept color=green!80!black] { node[concept] (ns) {Neuro\-science} }
      child { node[concept] {Func. Lung Imaging} }
      child { node[concept] {Breast} }
      child { node[concept] {Cardiac} }
    }  
    child[concept color=blue!80!black, yshift=0.25cm] {
      node[concept,scale=1.1] (stat) {Statistics}
      [clockwise from=-60]
      child { node[concept] {Linear Modeling} }
      child { node[concept] (ml) {Machine Learning} }
    }
    child[concept color=orange, yshift=-0.5cm] { 
      node[concept,scale=1.1] {Computer Science} 
        [clockwise from=-145]
        child { node[concept] (ad) {Algorithm Development}
           [clockwise from=-60]
           child { node[concept] (antsr) {\footnotesize ANTsR} }
           child { node[concept] {ANTs} }
           child { node[concept] {ITK} }
           }
        child { node[concept] (cp) {Computer Programming} }
        child { node[concept] (cc) {Cluster Computing} }
    };

		\newcommand{\connbluetoorange}{to[circle connection bar switch color=from (blue!80!black) to (orange)]}
		\newcommand{\connorangetoorange}{to[circle connection bar switch color=from (orange) to (orange)]}
		\newcommand{\conngreentoorange}{to[circle connection bar switch color=from (green!80!black) to (orange)]}

  \begin{pgfonlayer}{background}
      \path (ad) \connorangetoorange (cp);
      \path (stat) \connbluetoorange (antsr);
      \path (ns) \conngreentoorange (cc);
  \end{pgfonlayer}

%  \begin{pgfonlayer}{background}
%      \path (ml) \connbluetoorange (cs);
%  \end{pgfonlayer}

\end{tikzpicture}
}
\end{center}
\end{frame}

@@

\uncover<3->{
\node [mybox2, text width = 3.5cm, right of=ET] (ASL) {%
  \begin{center}
  \begin{tabular}{c}
  \includegraphics[height=2.75cm]{ASL.png} 
  \vspace{0.15cm}
  \end{tabular}
  \scriptsize{Automatic generation of clinical CBF maps from ASL}
  \end{center}
  };
\node[fancytitle](ASL_title) at (ASL.north) {\scriptsize ASL$\rightarrow$CBF};
\path[line] (max.south) edge [out= 310, in= 90] (ASL_title.north);
}

@@

\uncover<1->{    
    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm,xshift=1.5cm,yshift=-0.5cm ] (nirep) { 
        \begin{center}
			  \includegraphics[width=5.5cm]{NIREPLabels.png} \\
        \end{center}
			  };
}			  
\uncover<2->{    
    \path[->,rounded corners=0.1cm] 
      node[format, right of=nirep, xshift=2.25cm, yshift=1.85cm,text width=4.5cm] (rp) {
        \begin{center}
			  \includegraphics[width=4.5cm]{yylabel26_results.pdf}
        \end{center}
			  };
    \path[->,thick, color = yellow] (rp.west) edge [out= 180, in= 90] (1.25,0);			  
}			  
\uncover<3->{    
    \path[->,rounded corners=0.1cm] 
      node[format, right of=nirep, xshift=2.25cm, yshift=-1.85cm,text width=4.5cm] (rt) {
        \begin{center}
			  \includegraphics[width=4.5cm]{yylabel8_results.pdf} \\
        \end{center}
			  };
    \path[->,thick, color = yellow] (rt.west) edge [out= 180, in= 270] (1.4,-2.);
}			  
\uncover<4->{    
    \path[->,rounded corners=0.1cm] node[format,below of=nirep, text width = 4.0cm, yshift=1cm ] (wow) { 
        \begin{center}    
        {\color{yellow}{\em It takes $\sim$20--30 hours per subject!!}}
        \end{center}    
			  };
}			  
\end{tikzpicture}

@@

\uncover<1->{
    \path[->,rounded corners=0.1cm] node[text width=5cm,xshift = 1cm] (nlm) { 
        \begin{center}
			  \includegraphics[width=4.755cm]{visible_human_project.png} \\
        \end{center}
			  };
}			  
\uncover<2->{
    \path[->,rounded corners=0.1cm] 
        node[text width=6cm, right of=nlm, xshift=3cm, yshift=1.25cm] (logos) { 
        \begin{center}
			  \includegraphics[width=6cm]{logos.png} \\
        \end{center}
			  };
}			  
\uncover<3->{
    \path[->,rounded corners=0.1cm] node[text width=3cm, yshift=2cm, below of=logos] (itk) { 
        \begin{center}
			  \includegraphics[width=3.cm]{ITK.png} \\
        \end{center}
			  };
}			  
\uncover<4->{
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, yshift=1.2cm, below of=itk] (ants) { 
        \begin{center}
			  \includegraphics[width=2.1cm]{ANTsLogo.png} \\
        \end{center}
			  };
}			  
\uncover<5->{
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, yshift=1.2cm, below of=itk] (ants) { 
        \begin{center}
			  \includegraphics[width=2.1cm]{ANTsLogo.png} \\
        \end{center}
			  };
}

@@

\uncover<1->{			  
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, yshift = 2cm] (r16) { 
        \begin{center}
			  \includegraphics[width=2cm]{r16slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{387\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, right of=r16] (r27) { 
        \begin{center}
			  \includegraphics[width=2cm]{r27slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{392\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of=r16] (r30) { 
        \begin{center}
			  \includegraphics[width=2cm]{r30slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{406\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of=r27] (r62) { 
        \begin{center}
			  \includegraphics[width=2cm]{r62slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{411\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of = r30] (r64) { 
        \begin{center}
			  \includegraphics[width=2cm]{r64slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{425\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of=r62] (r85) { 
        \begin{center}
			  \includegraphics[width=2cm]{r85slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{430\_oasis}}
        \end{center}
			  };
}			  
\uncover<2->{			  
    \path[->,rounded corners=0.1cm] node[text width=6cm, xshift=2cm,right of=r62] (qstat) { 
        \begin{center}
			  \includegraphics[width=5.75cm]{qstat.png} \\
        \end{center}
			  };		
}

\uncover<3->{			  
  \path[->,thick, color = yellow, dashed] (0.5,2.3) edge [out=35,in= 145] (4.5,2.3);
  \path[->,thick, color = yellow, dashed] (3.1,1.55) edge [out=-35,in=-145] (4.5,1.55);
  \path[->,thick, color = yellow, dashed] (0.5,-0.25) edge [out=35,in= 145] (4.5,-0.25);
  \path[->,thick, color = yellow, dashed] (3.1,-0.9) edge [out=-35,in=-145] (4.5,-0.9);
  \path[->,thick, color = yellow, dashed] (0.5,-2.8) edge [out=35,in= 145] (4.5,-2.8);
}  
\uncover<4->{			  
  \path[->,thick, color = red, dashed] (3.1,-3.45) edge [out=-35,in=-145] (4.5,-3.45);
}

@@

\begin{frame}{Further information}

\begin{tikzpicture}[node distance=1cm, auto,>=latex', thin]
    % We need to set at bounding box first. Otherwise the diagram
    % will change position for each frame.
    \path[->,rounded corners=0.1cm] node[text width=2cm,xshift=-2cm] (ants) { 
        \begin{center}
			  \includegraphics[width=3.5cm]{ants2.png} \\
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=6cm, xshift=5cm, right of=ants] { 
        \begin{center}
        \begin{itemize}
          \item Insight Toolkit:  http://www.itk.org
          \item ANTs/ANTsR:  http://www.picsl.upenn.edu/ANTs/
          \item UVACSE:  http://www.uvacse.virginia.edu
        \end{itemize}
        \end{center}
			  };

>>>>

\documentclass[xcolor=dvipsnames,serif,10pt]{beamer}
\usepackage{etex}

@@

  \begin{columns}[c]
    \begin{column}{0.5\textwidth}
    \begin{center}  
      \includegraphics[width=5cm]{London_taxi.jpg}
    \end{center}
    \end{column}  
    \begin{column}{0.4\textwidth}
    \begin{center}  
      \vspace{-0.5cm}
      \includegraphics[width=5cm]{hippocampus.png} \\
      \pause
        \begin{align*}
			  SPM (1995):\,\,&   6418\,\,\text{citations}\\
			  VBM (2000):\,\,&   3593\,\,\text{citations}\\
			  Opt. VBM (2001):\,\,&  2353\,\,\text{citations}\\
			  TBSS (2006):\,\,&  1106\,\,\text{citations}\\
			  \end{align*}
      \vspace{0cm}
			  \highlight[yellow!100!black]{$6418 + 3593 + 2353 + 1106 = 13470\,\,\text{citations}$}
    \end{center}
    \end{column}  
  \end{columns}    
\end{frame}

@@

%\begin{frame}
%
%
%\tikzset{level 1 concept/.append style={font=\sf, sibling angle=135,level distance = 25mm}}
%\tikzset{level 2 concept/.append style={font=\sf, sibling angle=60,level distance = 15mm}}
%\tikzset{level 3 concept/.append style={font=\sf, sibling angle=60,level distance = 15mm}}
%\tikzset{every node/.append style={scale=0.5}}
%
%\begin{center}
%\resizebox{9cm}{7.5cm}{
%\begin{tikzpicture}
%  \path[mindmap,concept color=red!50!black,text=white]
%    node[concept,scale=0.9] {\Large Data Analysis}
%    [clockwise from=45]
%    child[concept color=green!50!black, yshift=-0.5cm] {
%      node[concept,scale=1.1] {Imaging Applications}
%      [clockwise from=120]
%      child[concept color=green!80!black] { node[concept] (ns) {Neuro\-science} }
%      child { node[concept] {Func. Lung Imaging} }
%      child { node[concept] {Breast} }
%      child { node[concept] {Cardiac} }
%    }  
%    child[concept color=blue!80!black, yshift=0.25cm] {
%      node[concept,scale=1.1] (stat) {Statistics}
%      [clockwise from=-60]
%      child { node[concept] {Linear Modeling} }
%      child { node[concept] (ml) {Machine Learning} }
%    }
%    child[concept color=orange, yshift=-0.5cm] { 
%      node[concept,scale=1.1] {Computer Science} 
%        [clockwise from=-145]
%        child { node[concept] (ad) {Algorithm Development}
%           [clockwise from=-60]
%           child { node[concept] (antsr) {\footnotesize ANTsR} }
%           child { node[concept] {ANTs} }
%           child { node[concept] {ITK} }
%           }
%        child { node[concept] (cp) {Computer Programming} }
%        child { node[concept] (cc) {Cluster Computing} }
%    };
%    
%		\newcommand{\connbluetoorange}{to[circle connection bar switch color=from (blue!80!black) to (orange)]}
%		\newcommand{\connorangetoorange}{to[circle connection bar switch color=from (orange) to (orange)]}
%		\newcommand{\conngreentoorange}{to[circle connection bar switch color=from (green!80!black) to (orange)]}
%
%  \begin{pgfonlayer}{background}
%      \path (ad) \connorangetoorange (cp);
%      \path (stat) \connbluetoorange (antsr);
%      \path (ns) \conngreentoorange (cc);
%  \end{pgfonlayer}
%    
%%  \begin{pgfonlayer}{background}
%%      \path (ml) \connbluetoorange (cs);
%%  \end{pgfonlayer}
%      
%\end{tikzpicture}
%}
%\end{center}
%\end{frame}

@@

\uncover<3->{
\node [mybox2, text width = 3.5cm, right of=ET] (ASL) {%
  \begin{center}
  \begin{tabular}{c}
  \includegraphics[height=2.5cm]{ASL.png} 
  \vspace{0.15cm}
  \end{tabular}
  \scriptsize{Automatic generation of clinical CBF maps from ASL}
  \end{center}
  };
\node[fancytitle](ASL_title) at (ASL.north) {\scriptsize ASL$\rightarrow$CBF};
\path[line] (max.south) edge [out= 310, in= 90] (ASL_title.north);
}

@@

\uncover<1->{    
    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm,xshift=1.5cm,yshift=-0.5cm ] (nirep) { 
        \begin{center}
			  \includegraphics[width=5.5cm]{NIREPLabels.png} \\
        \end{center}
			  };
}			  
\uncover<2->{    
    \path[->,rounded corners=0.1cm] 
      node[format, right of=nirep, xshift=2.25cm, yshift=1.85cm,text width=4.5cm] (rp) {
        \begin{center}
			  \includegraphics[width=4.5cm]{yylabel26_results.pdf}
        \end{center}
			  };
    \path[->,thick, color = yellow] (rp.west) edge [out= 180, in= 90] (1.25,0);			  
    \path[->,rounded corners=0.1cm] 
      node[format, right of=nirep, xshift=2.25cm, yshift=-1.85cm,text width=4.5cm] (rt) {
        \begin{center}
			  \includegraphics[width=4.5cm]{yylabel8_results.pdf} \\
        \end{center}
			  };
    \path[->,thick, color = yellow] (rt.west) edge [out= 180, in= 270] (1.4,-2.);
}			  
\uncover<3->{    
    \path[->,rounded corners=0.1cm] node[format,below of=nirep, text width = 4.0cm, yshift=1cm ] (wow) { 
        \begin{center}    
        {\color{yellow}{\em It takes $\sim$20--30 hours per subject!!}}
        \end{center}    
			  };
}			  
\end{tikzpicture}

@@

\uncover<1->{
    \path[->,rounded corners=0.1cm] node[text width=5cm,xshift = 1cm] (nlm) { 
        \begin{center}
			  \includegraphics[width=4.755cm]{visible_human_project.png} \\
        \end{center}
			  };
}			  
\uncover<2->{
    \path[->,rounded corners=0.1cm] 
        node[text width=6cm, right of=nlm, xshift=3cm, yshift=1.25cm] (logos) { 
        \begin{center}
			  \includegraphics[width=6cm]{logos.png} \\
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=3cm, yshift=2cm, below of=logos] (itk) { 
        \begin{center}
			  \includegraphics[width=3.cm]{ITK.png} \\
        \end{center}
			  };
}			  
\uncover<3->{
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, yshift=1.2cm, below of=itk] (ants) { 
        \begin{center}
			  \includegraphics[width=2.1cm]{ANTsLogo.png} \\
        \end{center}
			  };
}

@@

\uncover<1->{			  
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, yshift = 2cm] (r16) { 
        \begin{center}
			  \includegraphics[width=2cm]{r16slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{387\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, right of=r16] (r27) { 
        \begin{center}
			  \includegraphics[width=2cm]{r27slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{392\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of=r16] (r30) { 
        \begin{center}
			  \includegraphics[width=2cm]{r30slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{406\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of=r27] (r62) { 
        \begin{center}
			  \includegraphics[width=2cm]{r62slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{411\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of = r30] (r64) { 
        \begin{center}
			  \includegraphics[width=2cm]{r64slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{425\_oasis}}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=2.1cm, below of=r62] (r85) { 
        \begin{center}
			  \includegraphics[width=2cm]{r85slice.png} \\
			  \vspace{-0.5cm}
			  {\footnotesize \texttt{430\_oasis}}
        \end{center}
			  };
}			  
\uncover<2->{			  
    \path[->,rounded corners=0.1cm] node[text width=6cm, xshift=2cm,right of=r62] (qstat) { 
        \begin{center}
			  \includegraphics[width=5.75cm]{qstat.png} \\
        \end{center}
			  };		
  \path[->,thick, color = yellow, dashed] (0.5,2.3) edge [out=35,in= 145] (4.5,2.3);
  \path[->,thick, color = yellow, dashed] (3.1,1.55) edge [out=-35,in=-145] (4.5,1.55);
  \path[->,thick, color = yellow, dashed] (0.5,-0.25) edge [out=35,in= 145] (4.5,-0.25);
  \path[->,thick, color = yellow, dashed] (3.1,-0.9) edge [out=-35,in=-145] (4.5,-0.9);
  \path[->,thick, color = yellow, dashed] (0.5,-2.8) edge [out=35,in= 145] (4.5,-2.8);
  \path[->,thick, color = red, dashed] (3.1,-3.45) edge [out=-35,in=-145] (4.5,-3.45);
}

@@

\begin{frame}{}

\begin{tikzpicture}[node distance=1cm, auto,>=latex', thin]
    % We need to set at bounding box first. Otherwise the diagram
    % will change position for each frame.
    \path[->,rounded corners=0.1cm] node[text width=2cm,xshift=-2cm] (ants) { 
        \begin{center}
			  \includegraphics[width=3.5cm]{ants2.png} \\
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[text width=7cm, xshift=5.5cm, right of=ants] { 
        \begin{center}
        \begin{block}{Further information}
        \begin{itemize}
          \item \url{http://www.itk.org}
          \item \url{http://www.picsl.upenn.edu/ANTs}
          \item \url{http://www.uvacse.virginia.edu}
        \end{itemize}
        \end{block}
        \end{center}
			  };
